Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-07-04 paper/paper.tex
revision

If, however, we have not hit the @out@ cache, we retrieve the values from the @in@ cache, 
and update the @out@ cache with values from the @in@ cache. This retrieval from the @in@ 
cache may return an empty set of values if there is no such mapping for the configuration 
from the last iteration.
In reality, we first conservatively assume that all computations can be diverged, and if 
not, we update its values in the cache after the evaluation. In terms of partial orders and 
lattices, it is the case that starts the Kleene iteration from the bottom of the lattice.

@@

% TODO: summarize this section

>>>>

If, however, we have not hit the @out@ cache, we retrieve the values from the @in@ cache, 
and update the @out@ cache with values from the @in@ cache. This retrieval from the @in@ 
cache may return an empty set of values if there is no such mapping for this configuration 
from the previous iteration.
In the initial iteration, we first conservatively assume that all computations can be diverged, 
and if not, we update its values in the cache after the evaluation. In terms of partial orders and 
lattices, it is the case that starts the Kleene iteration from the bottom of the lattice.
The @out@ cache of this iteration will be used as @in@ cache for the next iteration.

@@

Now, what we have obtained is an abstract interpreter written in continuation-passing style.
Though the top-level function @aeval@ has only one continuation, but internally it uses
a @nd@ operator which is written with two layers of continuations. Further more, we added
a cache along with the interpreter and @nd@ operator.
